### 2011-10-28 inst/doc/article.Rnw
Added article and manual Rnw files

\begin{center}
\vspace*{1in}
\textbf{\Large QCL mapping in R }

@@

\textbf{\sffamily Abstract}: Introduction into quanitative correlation 
locus (QCL) mapping using the R package qcl
\vfill

@@

\textbf{\sffamily Introduction}
Some introduction text

@@

\textbf{\sffamily Format and load your data}
\nopagebreak

Loading your data

@@

\textbf{\sffamily QCLscan and QCLscan.network}
\nopagebreak

Explains how to map QCL using the QCLscan and QCLscan.network functions.

\bigskip
\textbf{\sffamily Significance using QCLpermute}
\nopagebreak

Explains how to determine QCL significance using the QCLpermute function.

\bigskip
\textbf{\sffamily Advanced plots and QCL networks}
\nopagebreak

Some more advanced topics

>>>>

\begin{center}
\vspace*{1in}
\textbf{\Large QCL mapping in experimental crosses}

@@

\textbf{\sffamily Abstract}: Quanitative correlation locus (QCL) mapping is 
a novel approach to detect genetic regulation of phenotypes in recombinant 
inbred line populations (RIL)
\vfill

@@

\textbf{\sffamily Introduction}

Some introduction text

@@

\textbf{\sffamily Methodology}
\nopagebreak

Some methodology text

@@

\textbf{\sffamily Results}
\nopagebreak

Some resulting text

\bigskip
\textbf{\sffamily Discussion}
\nopagebreak

Some discussion text
